\documentclass[11pt]{article}

\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{lipsum}

% ToC
\usepackage{blindtext} 
\usepackage[linktocpage]{hyperref}
\usepackage{bookmark}
\usepackage[compact]{titlesec}

% bib
%\usepackage[round]{natbib}
\usepackage[square,sort,numbers]{natbib}

% Math Imports
\usepackage{amsmath, amssymb, bm, fancyhdr, sectsty, dsfont, mathtools}

% Tikz
\usepackage{tikz}
\usetikzlibrary{bayesnet}
\usetikzlibrary{arrows}

\usepackage{wrapfig}
\usepackage{comment}
\usepackage{subcaption}
\usepackage{cleveref}

% Symbols
\newcommand\ind{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\newcommand\norm[1]{\left\lVert#1\right\rVert}
\newcommand\set[1]{\left\{#1\right\}}

\newcommand\RNN{\mathrm{RNN}}
\newcommand\MLP{\mathrm{MLP}}
\newcommand\enc{\mathrm{enc}}
\newcommand\softmax{\mathrm{softmax}}

% Distributions
\newcommand{\Cat}{\mathrm{Cat}}
\newcommand\Expo{\mathrm{Expo}}
\newcommand\Bern{\mathrm{Bern}}
\newcommand\Pois{\mathrm{Pois}}
\newcommand\Bin{\mathrm{Bin}}
\newcommand\Unif{\mathrm{Unif}}
\newcommand\Betad{\mathrm{Beta}}
\newcommand\Gammad{\mathrm{Gamma}}
\newcommand\Geom{\mathrm{Geom}}
\newcommand\Logd{\mathrm{Logistic}}

\newcommand\E[1]{\mathbb{E}\left[#1\right]}
\newcommand\Es[2]{\mathbb{E}_{#1}\left[#2\right]}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Cor}{\mathrm{Cor}}

% Bold stuff
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bd}{\mathbf{d}}
\newcommand{\be}{\mathbf{e}}
\newcommand{\bg}{\mathbf{g}}
\newcommand{\bh}{\mathbf{h}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bs}{\mathbf{s}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bz}{\mathbf{z}}

% mathcal stuff
\newcommand{\mcD}{\mathcal{D}}

% math blackboard bold stuff
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}


\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\titlespacing{\paragraph}{0pt}{*0}{*0}
%\setlength{\parskip}{-5mm plus1mm minus1mm}

\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage[displaymath,mathlines]{lineno}
\linenumbers

\begin{document}
\lhead{Justin Chiu}
\chead{2018 NDSEG Application}
\rhead{Personal Statement}

\begin{center}
%\textbf{Exploiting the Duality of Natural Language Generation and Understanding}
\textbf{Information Extraction with Weak Supervision}
\end{center}

In the past five years, the field of natural language processing (NLP)
neural network based methods have overwhelmingly dominated other approaches for many applications.
While flexible, neural network models are generally overparamaterized and take many examples to train.


\begin{enumerate}
\item Short term and long term goals
    \begin{enumerate}
    \item Long term goal: developing controllable LVMs for NLP.
        In particular, generative models whose latent structure can be interpreted
        for scientific inquiry, evaluation of causal mechanisms,
        model comparison, as well as control through intervention.
    \item Short term goal: advance principled inference methods for NLP.
        In particular, interested in applications where posterior inference is important:
        for example information extraction.
    \end{enumerate}
\item How did these goals develop?
    \begin{enumerate}
    \item How to incorporate context for translation and language modeling?
    \item What about the cognitive process behind language generation?
    \item Interest in fact-checking and argumentation.
    \end{enumerate}
\item How have I begun to lay foundation for these goals? (Resume blurbs)
    \begin{enumerate}
    \item SMT @ Penn, NYU, FAIR, translation, LM, neural networks
    \item LVMs and inference @ Harvard
    \end{enumerate}
\item How does the fellowship fit these goals
    \begin{enumerate}
    \item Allow me the freedom to freedom to devote my research to information extraction entirely?
    \item Knowledge graph completion.
    \item Developing technology for the country.
    \end{enumerate}
\end{enumerate}

\bibliographystyle{plainnat}
\bibliography{w}

\end{document}

